The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.

>>>>

Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
